---
title: "Regex"
author: "Tanner Ashurst"
date: "03/02/2021"
output: html_document
---
## Part 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Make sure to load all necessary libraries before beginning.
```{r, include = F}
library(dplyr)
```


To begin, we will import the measurements.csv file into an object titled "MData."
```{r}
MData <- read.csv("./measurements.csv")
print(MData)
```

Next, we will add a new column called "Sp" which shortens the genus name in the "Organism" column to only the first letter and period.
```{r}
MData <- MData %>% mutate(Sp = gsub('^(\\w)\\w+', '\\1.',  MData$Organism))
print(MData)
```

Now, we will create a new dataset where the "Sp" column has replaced the "Organism" column.
```{r}
NewData <- MData %>% select('Sp', 'Limb.width', 'Limb.length', 'Observer')
print(NewData)
```

And now we will save this new dataset as "MeasShort.csv."
```{r}
write.csv(NewData, "MeasShort.csv")
```

## Part 2

We will now write a bash script called MyCount.sh that will loop through a sequence of 20 numbers and for each number it will report the respective number and whether it is a single- or double-digit number.

```{r}
for Count in {1..20}
do
  echo 'This is loop number $Count'
done
```

